Our Title

### 2015-04-30 draft.tex
Updated figure references.

 \begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 5.9cm 0cm 5.35cm, clip,scale=0.6]{../figures/ISILRelationships.pdf}
   \caption{ISIL relationships as of mid-2014.  Note the figure uses the alternative name of ISIL that was preferred by the Obama administration for ISIL \cite{NationalConsortiumfortheStudyofTerrorismandResponsestoTerrorism2014}}
     \label{fig:ISILRelationships}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[scale=0.4]{../figures/affmap.png}
   \caption{Map of countries with ISIL affiliates \cite{IntelCenter2015}. }
     \label{fig:affmap}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{../figures/structure_infographic.jpg}
   \caption{Structure of the Office of the Director of National Intelligence \cite{OfficeoftheDirectorofNationalIntelligence}}
     \label{fig:structure_infographic}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 2cm, clip,scale=0.6]{../figures/det_time.png}
   \caption{Table of distance and time needed to detect Weapons Grade  material with a tamper, where detection is considered when the counts are 5 standard deviations above the background. \cite{Fetter1990}}
     \label{fig:det_time}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0.1cm 0cm 0cm, clip,scale=0.4]{../figures/shield_time.png}
   \caption{Time needed to reach a gamma count of highly enriched uranium (HEU) 5 standard deviations above the background for a given lead shield thickness \cite{Glaser2007}.}
     \label{fig:shield_time}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{../figures/NRF_setup.png}
   \caption{A typical set-up for  a nuclear resonance fluorescence system \cite{Morse2014a}.}
     \label{fig:NRF_setup}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 5cm 18.7cm 5cm 5cm, clip,scale=1]{../figures/Chichester_timing.pdf}
   \caption{Representative pattern for pulsed neutron beam and when specific signatures can be expected \cite{Chichester2009}.}
     \label{fig:Chichester_timing}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[trim = 3cm 11.3cm 3cm 10.5cm, clip,scale=1]{../figures/Chichester_counts.pdf}
   \caption{Counts over time for HEU, depleted uranium, and Pu in a wooden cube \cite{Chichester2009}.}
     \label{fig:Chichester_counts}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.5]{../figures/shielding_reqs.jpg}
   \caption{Schematic representation of the shielding requirements of alpha, beta, and gamma radiation. }
     \label{fig:shielding_reqs}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{../figures/current_territory.png}
   \caption{Current ISIL Territory}
     \label{fig:current_territory}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{../figures/current2.png}
   \caption{My Caption \cite{Lewis2014}}
     \label{fig:current2}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.4]{../figures/oil_reserves.png}
   \caption{Oil Reserves and Ground Transportation Routes}
     \label{fig:oil_reserves}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{../figures/oil_infrastructure.jpg}
   \caption{My caption}
     \label{fig:oil_infrastructure}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.7]{../figures/minerals.jpg}
   \caption{Mineral Deposits and Industry in Iraq}
     \label{fig:minerals}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.6]{../figures/elec_grid.jpg}
   \caption{Iraqi Electricity Grid}
     \label{fig:elec_grid}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.6]{../figures/nuke_facilities.jpg}
   \caption{Iraq Declared Nuclear Facilities (as of 2002)}
     \label{fig:nuke_facilities}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=1]{../figures/syria_minerals.jpg}
   \caption{Mineral Deposits and Industry in Syria}
     \label{fig:syria_minerals}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=1]{../figures/syria_grid.png}
   \caption{Syrian Electricity Grid}
     \label{fig:syria_grid}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{../figures/syria_nuke_facilities.jpg}
   \caption{Syrian sites of possible nuclear facilities}
     \label{fig:syria_nuke_facilities}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{../figures/seizures.png}
   \caption{Location and time of global seizures of special nuclear materials \cite{Muller2007}.}
     \label{fig:seizures}
\end{figure}

>>>>

 \begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 5.9cm 0cm 5.35cm, clip,scale=0.6]{./figures/ISILRelationships.pdf}
   \caption{ISIL relationships as of mid-2014.  Note the figure uses the alternative name of ISIL that was preferred by the Obama administration for ISIL \cite{NationalConsortiumfortheStudyofTerrorismandResponsestoTerrorism2014}}
     \label{fig:ISILRelationships}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[scale=0.4]{./figures/affmap.png}
   \caption{Map of countries with ISIL affiliates \cite{IntelCenter2015}. }
     \label{fig:affmap}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{./figures/structure_infographic.jpg}
   \caption{Structure of the Office of the Director of National Intelligence \cite{OfficeoftheDirectorofNationalIntelligence}}
     \label{fig:structure_infographic}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 2cm, clip,scale=0.6]{./figures/det_time.png}
   \caption{Table of distance and time needed to detect Weapons Grade  material with a tamper, where detection is considered when the counts are 5 standard deviations above the background. \cite{Fetter1990}}
     \label{fig:det_time}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0.1cm 0cm 0cm, clip,scale=0.4]{./figures/shield_time.png}
   \caption{Time needed to reach a gamma count of highly enriched uranium (HEU) 5 standard deviations above the background for a given lead shield thickness \cite{Glaser2007}.}
     \label{fig:shield_time}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{./figures/NRF_setup.png}
   \caption{A typical set-up for  a nuclear resonance fluorescence system \cite{Morse2014a}.}
     \label{fig:NRF_setup}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 5cm 18.7cm 5cm 5cm, clip,scale=1]{./figures/Chichester_timing.pdf}
   \caption{Representative pattern for pulsed neutron beam and when specific signatures can be expected \cite{Chichester2009}.}
     \label{fig:Chichester_timing}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[trim = 3cm 11.3cm 3cm 10.5cm, clip,scale=1]{./figures/Chichester_counts.pdf}
   \caption{Counts over time for HEU, depleted uranium, and Pu in a wooden cube \cite{Chichester2009}.}
     \label{fig:Chichester_counts}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.5]{./figures/shielding_reqs.jpg}
   \caption{Schematic representation of the shielding requirements of alpha, beta, and gamma radiation. }
     \label{fig:shielding_reqs}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.6]{./figures/current_territory.png}
   \caption{Current ISIL Territory}
     \label{fig:current_territory}
\end{figure}

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/current2.png}
   \caption{My Caption \cite{Lewis2014}}
     \label{fig:current2}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.4]{./figures/oil_reserves.png}
   \caption{Oil Reserves and Ground Transportation Routes}
     \label{fig:oil_reserves}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.3]{./figures/oil_infrastructure.jpg}
   \caption{My caption}
     \label{fig:oil_infrastructure}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.7]{./figures/minerals.jpg}
   \caption{Mineral Deposits and Industry in Iraq}
     \label{fig:minerals}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.6]{./figures/elec_grid.jpg}
   \caption{Iraqi Electricity Grid}
     \label{fig:elec_grid}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=.6]{./figures/nuke_facilities.jpg}
   \caption{Iraq Declared Nuclear Facilities (as of 2002)}
     \label{fig:nuke_facilities}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=1]{./figures/syria_minerals.jpg}
   \caption{Mineral Deposits and Industry in Syria}
     \label{fig:syria_minerals}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=1]{./figures/syria_grid.png}
   \caption{Syrian Electricity Grid}
     \label{fig:syria_grid}
\end{figure}

@@

\begin{figure}[H]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{./figures/syria_nuke_facilities.jpg}
   \caption{Syrian sites of possible nuclear facilities}
     \label{fig:syria_nuke_facilities}
\end{figure}

@@

\begin{figure}[h]
 \centering
 \includegraphics[trim = 0cm 0cm 0cm 0cm, clip,scale=0.7]{./figures/seizures.png}
   \caption{Location and time of global seizures of special nuclear materials \cite{Muller2007}.}
     \label{fig:seizures}
\end{figure}
